PS753 Glossary

### 2022-01-31 _academics/ps753-glossary/ps753-glossary.Rmd
Add Borgatti terms

>>>>

### @borgatti2009

sociometry
: "a technique for eliciting and graphically representing individuals' subjective feelings toward one another"

strength of weak ties (SWT) theory
: the theory that one is likelier to hear new information from people they aren't closely connected to in a network (c.f. homiphily)

centrality
: a family of positional properties of nodes in a network

Freeman's betweenness
: a type of centrality where a node is frequently along the shortest path between pairs of nodes, giving control over flow or power

opportunity-based antecedents
: "the likelihood that two nodes will come into contact" - when considering the formation of ties

benefit-based antecedents
: "some kind of utility maximization or discomfort minimization that leads to tie formation"

node homogeneity
: a category of node outcomes referring to the similarity of nodes

performance
: a category of node outcomes referring to some good (such as strong performance)
